How to Avoid OOTA Without Really Trying

### 2024-10-02 paper/ootavacuous.tex
ootavacuous: Shorten last sentence of first paragraph
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\emph{Tagline: ``Need to look at both source code and machine code.''}

@@

The outcome when a given computer executes the machine code in a file
has historically been much better defined than the executions of the
C++ abstract machine.
The hardware's behavior is typically specified with great precision by
the designer or manufacturer, and there are formal, executable memory models
describing exactly what patterns of loads and stores can occur.
Thus, leaving aside questions of asynchronous interrupts and system
calls, the behavior of a CPU executing a particular thread within a
program is entirely determined by the values obtained by the various
memory-load instructions.\footnote{
	We regard read-modify-write instructions as consisting of both a
	memory load and a memory store.}

>>>>

@@

The outcome when a given computer executes the machine code in a file
has historically been much better defined than the executions of the
C++ abstract machine.
The hardware's behavior is typically specified with great precision by
the designer or manufacturer, and there are formal, executable memory models
describing exactly what patterns of loads and stores can occur.
Thus, leaving aside asynchronous interrupts and system
calls, the behavior of a CPU executing a particular thread within a
program is entirely determined by the values obtained by its
memory-load instructions.\footnote{
	We regard read-modify-write instructions as consisting of both a
	memory load and a memory store.}
